---
output: rmarkdown::github_document
---

# urldiversity

Quantify 'URL' Diversity and Apply Popular Biodiversity Indices to a 'URL' Collection

## Description

Methods are provided to compute the 'WSDL Diversity Index' <http://ws-dl.blogspot.com/2018/05/2018-05-04-exploration-of-url-diversity.html> 
along with selected biodiversity indidces to a corpus (collection) of 'URLs'.

## NOTE

All credit goes to [Alexander Nwala](http://www.cs.odu.edu/~anwala/) for the algorithm research and [original Python implementation](https://github.com/anwala/url-diversity).
   
## TODO

- [ ] Handle some edge cases
- [ ] Tests
- [ ] Better documentation
- [ ] Vignette with many citations from the WSDL blog post

## What's Inside The Tin

The following functions are implemented:

### Core function:

- `uri_diversity`:	Quantify URL diversity
- `url_diversity`:	(an alias for ^^ b/c I regularly forget it's rightlfully `uri`)

### Processing Helpers:

- `clean_index_factors`:	Clean up diversity and evenness names

### Scraping Helpers:

- `body_anchor_urls`:	Extract all body anchor hypertext references
- `body_img_urls`:	Extract all body image URLs
- `safeGET`:	Safer version of 'httr::GET()'
- `safePOST`:	Safer version of 'httr::POST()'

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/urldiversity")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(urldiversity)

# current verison
packageVersion("urldiversity")

```

```{r}
collection <- readLines(system.file("extdat", "corpus.txt", package = "urldiversity"))

print(collection)

x <- uri_diversity(collection)

dplyr::glimpse(x)

x
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.